### 2015-02-28 icfp15-servo/servo.tex
Promote LLVM from a footnote to a reference

There are two limitations in the language interoperability that pose challenges for Servo today.
First, Rust cannot currently expose varargs-style functions to C code.
Second, Rust cannot compile against \Cplusplus{} code.
In both cases, Servo uses C wrapper code to call into the code that Rust cannot directly
reach.
While this approach is not a large problem for varargs-style functions, it defeats many of the
places where the \Cplusplus{} code has been crafted to ensure the code is inlined into the caller,
resulting in degraded performance. We intend to fix this through cross-language inlining, taking
advantage of the fact that both \lstinline{rustc} and \lstinline{clang++} can produce output in the
LLVM\footnote{\url{http://llvm.org}} intermediate representation, which is subject to link-time
optimization. We have demonstrated this capability at small scale, but have not yet deployed it
within Servo.

>>>>

There are two limitations in the language interoperability that pose challenges for Servo today.
First, Rust cannot currently expose varargs-style functions to C code.
Second, Rust cannot compile against \Cplusplus{} code.
In both cases, Servo uses C wrapper code to call into the code that Rust cannot directly
reach.
While this approach is not a large problem for varargs-style functions, it defeats many of the
places where the \Cplusplus{} code has been crafted to ensure the code is inlined into the caller,
resulting in degraded performance. We intend to fix this through cross-language inlining, taking
advantage of the fact that both \lstinline{rustc} and \lstinline{clang++} can produce output in the
LLVM intermediate representation~\cite{LLVM}, which is subject to link-time optimization. We have
demonstrated this capability at small scale, but have not yet deployed it within Servo.
